Predicting job success from developer's profile

### 2017-02-15 Paper/MSRChallenge2017.tex
added some approach

\begin{enumerate}
\item What is the relationship, if any, between attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the travis jobs this commit triggers?
\item Given a dataset described before, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power of a linear regression model created from this data?
\item Which attributes (in social data, technical data, and both together) are the most decisive in order to know if a commit will be successful or not?
\item Does any of the social attributes have a significant impact in the likelihood of commit success?

@@

To do this, we extracted from the original file provided~\cite{msr17challenge} the commit hash and the project name. We removed the repeated rows and created a script to gather the social data of the developer who pushed that commit.
First we concatenated the two attributes before mentioned in the following way:
\newline \newline
\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
\newline \newline
We created a script that takes this string and navigates through the html representation of the website described above, and looks for the \textit{username} of the developer in the Github platform. If it is able to find one, we then create another string following the pattern:
\newline \newline
\textit{https://github.com/\textbf{UserName}}
\newline \newline
We then navigate through the html representation of the developer's profile website (described above) and look for the following attributes:
\begin{itemize}
\item repositories
\item stars
\item followers
\item following
\item collabProjects
\end{itemize}

To this dataset, we also added from the dataset provided~\cite{msr17challenge} the attribute gh\_by\_core\_team\_member which we considered to have also social weight.

@@

\section{Multiple linear regression}
How we used the ML

\section{Evaluation}
Maybe a 10 fold cross validation?

>>>>

\begin{enumerate}
\item What is the relationship, if any, between attributes that describe the complexity of a commit (such as files added, tests added, lines of code, etc) and the final status of the Travis jobs this commit triggers?
\item Given the dataset described before, is the social data gathered from the online profiles of developers who pushed those commits, able to increase the predictive power of a linear regression model created from this dataset?
\item Which attributes (in social data, technical data, and both together) are the most decisive in order to know if a commit will be successful or not?
\item Does any of the social attributes have a significant impact in the likelihood of commit integration success?

@@

To do this, we extracted from the original file provided~\cite{msr17challenge} the commit hash and the project name. We removed the repeated rows and created a script to gather the social data of the developer who pushed that commit.
First we concatenated the two attributes before mentioned in the following way:
\newline \newline
\textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
\newline \newline
We created a script that constructs this string and navigates through the html representation of the website described above, and looks for the \textit{username} of the developer in the Github platform. If it is able to find one, we then create another string following the pattern:
\newline \newline
\textit{https://github.com/\textbf{UserName}}
\newline \newline
We then navigate through the html representation of the developer's profile website (described above) and gather the following attributes:
\begin{itemize}
\item Repositories
\item Stars
\item Followers
\item Following
\item ContribProjects
\end{itemize}

Repositories alludes to the repositories the developer has access to. This includes where the developer is the repository owner,where the developer is a collaborator, and repositories that the developer can access through an organization membership.\footnote{https://developer.github.com/v3/repos/} Stars show the projects the developer has stared, where starring translates to showing appreciation to the repository and creating a bookmark for later access.\footnote{https://help.github.com/articles/about-stars/} Followers and Following detail the number of developers that are following and being followed by the developer in question. Finally, the last attribute studies is the number of contributions made by the developer in the last year. To this dataset, we also added from the original dataset provided~\cite{msr17challenge} the attribute gh\_by\_core\_team\_member which we considered to have also social weight, which describes if the developer pushing the commit is a core member of the project the commit is being pushed to.

@@

\section{Evaluation}
Logistic Regression and Decision trees.
